---
title: "Make Fake Data"
output: html_notebook
---

# Overhead
```{r overhead, include = FALSE}
packages_vector <- c("tidyverse",
                     "googledrive")

need_to_install <- packages_vector[!(packages_vector %in% installed.packages()[,"Package"])]

if (length(need_to_install)) install.packages(need_to_install)

for (package in packages_vector){
  library(package, character.only = TRUE)
}

```

# Remote I-O
```{r remote-io}
external_dir <- "../../data/external/"
interim_dir <- "../../data/interim/"
google_drive_path <- "~/project_chandra_bot/"

first_name_file_name <- "https://raw.githubusercontent.com/smashew/NameDatabases/master/NamesDatabases/first%20names/us.txt"

last_name_file_name <- "https://raw.githubusercontent.com/smashew/NameDatabases/master/NamesDatabases/surnames/us.txt"

article_titles_file_name <- paste0(external_dir, "random_article_titles.txt")

output_file_name <- "fake_data.csv"

```

# Parameters
```{r parameters}

```

article_title = A,
         article_type = B,
         required_reviewers = C,
         reviewer_number = D,
         confidential_comments = E,
         reviewer_comments_to_author = F,
         reviewer_recommendation = G,
         review_complete = H,
         editorial_status = I,
         overall_score_for_presentation = 
         reviewer_name

# Data Reads
```{r data-reads}
raw_first_names_df <- read_csv(first_name_file_name, col_names = FALSE, col_types = "c")
raw_last_names_df <- read_csv(last_name_file_name, col_names = FALSE, col_types = "c")

# titles data not in quotes
input_line <- readLines(article_titles_file_name)
raw_article_titles_df <- tibble(title = input_line)

```

# Clean Data
```{r clean-data}
first_names_df <- raw_first_names_df %>%
  rename(first = X1)

last_names_df <- raw_last_names_df %>%
  rename(last = X1)

article_titles_df <- raw_article_titles_df %>%
  mutate(length = str_length(title)) %>%
  filter(length > 4)

remove(raw_first_names_df, raw_last_names_df, raw_article_titles_df)

```

# TODO:
1. Use random sentences for reviews.
2. Build methods to create a name
3. Start with database of finite set of humans
4. Combine N humans to write a paper
5. Reviewers get random sentences
6. Write a method to create a database entry, then make a million of them

