---
html_document:
  theme: cosmo
  toc: yes
output:
  html_document:
    df_print: paged
title: "Common Corridor Languages"
---

## Administration

#### Purpose
Understand the common languages used in the Utica Avenue corridor to inform the survey preparation. 

## Action

#### Overhead
```{r overhead, include = FALSE}
# install and load libraries
packages_vector <- c("tidyverse",
                     "googledrive",
                     "fuzzyjoin")

need_to_install <- packages_vector[!(packages_vector %in% installed.packages()[,"Package"])]

if (length(need_to_install)) install.packages(need_to_install)

for (package in packages_vector){
  library(package, character.only = TRUE)
}

```

#### Remote I/O
```{r remote-io}
google_drive_path <- "~/project_chandra_bhat/"
google_drive_files_df <- data.frame(file_name = c("reviewer_2016.csv", "reviewer_2017.csv", "reviewer_2018.csv"),
                                    year = c(2016, 2017, 2018),
                                    type = c("reviewer", "reviewer", "reviewer"),
                                    stringsAsFactors = FALSE)

for (reviewer_file in filter(google_drive_files_df, type == "reviewer")$file_name) {
  drive_download(file = drive_get(reviewer_file)$name, overwrite = TRUE)
}
```

#### Data Reads
```{r data-reads}
if (exists("running_df")) remove(running_df)
for (reviewer_file in filter(google_drive_files_df, type == "reviewer")$file_name) {
  
  input_year <- filter(google_drive_files_df, file_name == reviewer_file)$year
  
  working_df <- read_csv(reviewer_file, 
                         col_names = c("last_comma_first", "first", "last", "affiliation", "email"),
                         col_types = c(col_character(), col_character(), col_character(), 
                                       col_character(), col_character())) %>%
    mutate(year = input_year) %>%
  filter(!(email =="y.zeinali@gmail.com"))
  
  if (exists("running_df")) {
    running_df <- bind_rows(running_df, working_df)
  } else {
    running_df <- working_df
  }
}

raw_reviewer_df <- running_df

remove(running_df, working_df)

```

#### Data Reductions
Target:
name
aliases
hash_id
current_affiliation
phd_affiliation
google_scholar_url
google_scholar_citations
google_scholar_h_index
google_scholar_i10_index
```{r data-reductions}
working_df <- raw_reviewer_df %>%
  separate(last_comma_first, into = c("last", "first"), sep = ",", remove = TRUE) %>%
  mutate(name = trimws(paste0(first, " ", last))) %>%
  arrange(name, -year) %>%
  mutate(affiliation = ifelse(is.na(affiliation), "Missing", affiliation)) %>%
  group_by(name) %>%
  mutate(affil_change = (affiliation == lag(affiliation))) %>%
  filter(is.na(affil_change) | (!affil_change)) %>%
  mutate(affiliations = paste(affiliation, collapse = ";")) %>%
  ungroup() %>%
  separate(affiliations, into = c("current_affiliation", "previous_affiliations"), sep = ";", extra = "merge", fill = "right") %>%
  filter(is.na(affil_change)) %>%
  select(name, current_affiliation, previous_affiliations, email) %>%
  mutate(current_affiliation = ifelse(current_affiliation == "Missing", NA, current_affiliation)) %>%
  mutate(previous_affiliations = ifelse(previous_affiliations == "Missing", NA, previous_affiliations))

with_duplicates_df <- working_df

remove(working_df)
```

### Canonical Names
```{r canonical-names}
name_01_df <- with_duplicates_df %>%
  select(name_01 = name)

name_02_df <- with_duplicates_df %>%
  select(name_02 = name)

alias_finder_df <- stringdist_inner_join(name_01_df, name_02_df, by = c("name_01" = "name_02"), max_dist = 1) %>%
  group_by(name_01) %>%
  summarise(count = n()) %>%
  filter(count > 1)

alias_finder_df

# manually build aliases
alias_names_df <- data.frame(name = c("Bruce Appleyard", "Khander Nurul Habib", 
                                      "Rafael Maldonado Hinarejos", "Scott LeVine", 
                                      "Tomás Ruiz", "Bayarmaa Aleksandr", "José Holguín-Veras",
                                      "Chun-Hung Chen", "P. Christopher Zegras", "T. Keith Lawton"),
                             alias = c("Bruce Apppleyard", "Khandker Nurul Habib", 
                                       "Rafael Maldonado-Hinarejos", "Scott Le Vine", 
                                       "Tomas Ruiz", "Bayarmaa Alexandr", "Jose Holguin-Veras",
                                       "Chun-Hung Peter Chen", "P. Zegras", "T. Lawton"),
                             stringsAsFactors = FALSE)

canonical_names_df <- with_duplicates_df %>%
  filter(!(name %in% alias_names_df$alias)) %>%
  left_join(., alias_names_df, by = c("name")) %>%
  select(name, aliases = alias)

remove(alias_names_df, alias_finder_df, name_01_df, name_02_df)

```

### Canonical Affiliations
```{r canonical-affils}
affil_df <- with_duplicates_df %>%
  separate(previous_affiliations, into = c("prev_01", "prev_02", "prev_03"), sep = ";", extra = "merge", fill = "right")

current_df <- affil_df %>%
  filter(!is.na(current_affiliation)) %>%
  filter(!is.na(prev_01)) %>%
  select(current_affiliation)

prev_df <- affil_df %>%
  filter(!is.na(current_affiliation)) %>%
  filter(!is.na(prev_01)) %>%
  select(prev_01)

## GS Update

alias_finder_df <- stringdist_inner_join(current_df, prev_df, by = c("current_affiliation" = "prev_01"), max_dist = 7) %>%
  filter(!(current_affiliation == prev_01)) %>%
  group_by(current_affiliation, prev_01) %>%
  summarise(count = n()) %>%
  filter(count > 1)

alias_finder_df

## GS Update
alias_affils_df <- data.frame(affiliation = c("Aalto University",
                                              "California State Polytechnic University, Pomona",
                                              "CH2MHILL",
                                              "ETHZ - Swiss Federal Institute of Technology",
                                              "Gannett Fleming, Inc.",
                                              "Hasselt University",
                                              "HDR, Inc.",
                                              "Indian Institute of Technology, Madras",
                                              "Institute for Transportation Research and Education",
                                              "KTH Royal Institute of Technology",
                                              "World Bank",
                                              "University of California, Los Angeles",
                                              "University of Central Florida",
                                              "University of Louisiana",
                                              "Virginia Polytechnic Institute and State University",
                                              "WSP|Parsons Brinckerhoff",
                                              "Office of the Assistant Secretary for Research and Technology",
                                              "University of Maryland",
                                              "University of Massachusetts",
                                              "University of Michigan",
                                              "University of Minnesota",
                                              "New York City Transit",
                                              "Northwestern University",
                                              "Parsons",
                                              "Technical University of Berlin",
                                              "University of Vermont",
                                              "No Affiliation",
                                              "Imperial College London",
                                              "Independent",
                                              "University of Leeds",
                                              "Universidade de Sao Paulo",
                                              "University of Alabama",
                                              "University of Texas, El Paso"),
                              alias_01 = c("Aalto University School of Science and Technology",
                                           "California Polytechnic State University, Pomona",
                                           "CH2M",
                                           "ETH - Swiss Federal Institute of Technology",
                                           "Gannett Fleming Transit and Rail Systems",
                                           "IMOB, Hasselt University",
                                           "HDR",
                                           "Indian Institute of Technology, Madras (IIT)",
                                           "Inst. for Transportation Research and Education",
                                           "Royal Institute of Technology",
                                           "The World Bank",
                                           "University of California, Los Angeles (UCLA)",
                                           "University of Central Florida (UCF)",
                                           "University of Louisiana, Lafayette",
                                           "Virginia Polytechnic Institute & State University",
                                           "Parsons Brinckerhoff",
                                           "Office of the Assistant Secretary for Research and Technology (OST-R)",
                                           "University of Maryland, College Park",
                                           "University of Massachusetts, Amherst",
                                           "University of Michigan, Ann Arbor",
                                           "University of Minnesota, Twin Cities",
                                           "MTA New York City Transit",
                                           "Northwestern University Transportation Library",
                                           "Parsons Transportation Group, Inc.",
                                           "Technische Universitaet Berlin",
                                           "University of Vermont Transportation Research Center",
                                           "unaffiliated",
                                           "Imperial College of London",
                                           "Independent Consultant",
                                           "Institute for Transport Studies and Choice Modelling Centre, University of Leeds",
                                           "Universidade de Sao Paulo - USP",
                                           "University of Alabama, Tuscaloosa",
                                           "The University of Texas at El Paso (UTEP)"),
                              alias_02 = c(NA,
                                           NA,
                                           NA,
                                          "IVT ETHZ",
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           "University of Central Florida (UCF",
                                           NA,
                                           NA,
                                           "WSP Analysis & Strategy",
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA, 
                                           "No company",
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA),
                              alias_03 = c(NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           "No Organization",
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA),
                              alias_04 = c(NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           "Missing",
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA,
                                           NA),
                              stringsAsFactors = FALSE)

unique_affils_vector <- with_duplicates_df %>%
  select(-name) %>%
  separate(previous_affiliations, into = c("prev_01", "prev_02", "prev_03"), sep = ";", extra = "merge", fill = "right") %>%
  gather(key = "delete", value = "affiliation", na.rm = TRUE) %>%
  arrange(affiliation) %>%
  .$affiliation

canonical_affils_df <- data.frame(affiliation = unique(unique_affils_vector), stringsAsFactors = FALSE) %>%
  filter(!is.na(affiliation)) %>%
  filter(!(affiliation %in% alias_affils_df$alias_01)) %>%
  filter(!(affiliation %in% alias_affils_df$alias_02)) %>%
  filter(!(affiliation %in% alias_affils_df$alias_03)) %>%
  filter(!(affiliation %in% alias_affils_df$alias_04)) %>%
  left_join(., alias_affils_df, by = c("affiliation")) %>%
  mutate(affiliation_aliases = ifelse(is.na(alias_01), NA, alias_01)) %>%
  mutate(affiliation_aliases = ifelse(is.na(alias_02), 
                                              affiliation_aliases, 
                                              paste(affiliation_aliases, alias_02, sep = ";"))) %>%
  mutate(affiliation_aliases = ifelse(is.na(alias_03), 
                                              affiliation_aliases, 
                                              paste(affiliation_aliases, alias_03, sep = ";"))) %>%
  mutate(affiliation_aliases = ifelse(is.na(alias_04), 
                                              affiliation_aliases, 
                                              paste(affiliation_aliases, alias_04, sep = ";"))) %>%
  select(affiliation, affiliation_aliases)

remove(affil_df, alias_affils_df, alias_finder_df, unique_affils_vector, current_df, prev_df)

```


### Remove Duplicates with Canonical - GS Update
```{r deal-dups}
affils_join_df <- canonical_affils_df %>%
  separate(affiliation_aliases, into = c("affil_alias_01", "affil_alias_02","affil_alias_03", "affil_alias_04" ), sep = ";", extra = "merge", fill = "right") %>%
  mutate(affil_alias_01 = ifelse(is.na(affil_alias_01), "Missing", affil_alias_01)) %>%
  mutate(affil_alias_02 = ifelse(is.na(affil_alias_02), "Missing", affil_alias_02)) %>%
  mutate(affil_alias_03 = ifelse(is.na(affil_alias_03), "Missing", affil_alias_03)) %>%
  mutate(affil_alias_04 = ifelse(is.na(affil_alias_04), "Missing", affil_alias_04)) 
  

no_duplicates_df <- left_join(canonical_names_df, with_duplicates_df, by = c("name")) %>%
  mutate(current_affiliation = ifelse(is.na(current_affiliation), "None", current_affiliation)) %>%
  mutate(previous_affiliations = str_replace_all(previous_affiliations, "Missing", "None")) %>%
  separate(previous_affiliations, into = c("prev_01", "prev_02", "prev_03"), sep = ";", extra = "merge", fill = "right") %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_01), by = c("current_affiliation" = "affil_alias_01")) %>%
  mutate(current_affiliation = ifelse(is.na(affiliation), current_affiliation, affiliation)) %>%
  select(-affiliation) %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_02), by = c("current_affiliation" = "affil_alias_02")) %>%
  mutate(current_affiliation = ifelse(is.na(affiliation), current_affiliation, affiliation)) %>%
  select(-affiliation) %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_03), by = c("current_affiliation" = "affil_alias_03")) %>%
  mutate(current_affiliation = ifelse(is.na(affiliation), current_affiliation, affiliation)) %>%
  select(-affiliation) %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_04), by = c("current_affiliation" = "affil_alias_04")) %>%
  mutate(current_affiliation = ifelse(is.na(affiliation), current_affiliation, affiliation)) %>%
  select(-affiliation) %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_01), by = c("prev_01" = "affil_alias_01")) %>%
  mutate(prev_01 = ifelse(is.na(affiliation), prev_01, affiliation)) %>%
  select(-affiliation) %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_02), by = c("prev_01" = "affil_alias_02")) %>%
  mutate(prev_01 = ifelse(is.na(affiliation), prev_01, affiliation)) %>%
  select(-affiliation) %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_03), by = c("prev_01" = "affil_alias_03")) %>%
  mutate(prev_01 = ifelse(is.na(affiliation), prev_01, affiliation)) %>%
  select(-affiliation) %>%
    left_join(., select(affils_join_df, affiliation, affil_alias_04), by = c("prev_01" = "affil_alias_04")) %>%
  mutate(prev_01 = ifelse(is.na(affiliation), prev_01, affiliation)) %>%
  select(-affiliation) %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_01), by = c("prev_02" = "affil_alias_01")) %>%
  mutate(prev_02 = ifelse(is.na(affiliation), prev_02, affiliation)) %>%
  select(-affiliation) %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_02), by = c("prev_02" = "affil_alias_02")) %>%
  mutate(prev_02 = ifelse(is.na(affiliation), prev_02, affiliation)) %>%
  select(-affiliation) %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_03), by = c("prev_02" = "affil_alias_03")) %>%
  mutate(prev_02 = ifelse(is.na(affiliation), prev_02, affiliation)) %>%
  select(-affiliation) %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_04), by = c("prev_02" = "affil_alias_04")) %>%
  mutate(prev_02 = ifelse(is.na(affiliation), prev_02, affiliation)) %>%
  select(-affiliation) %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_01), by = c("prev_03" = "affil_alias_01")) %>%
  mutate(prev_03 = ifelse(is.na(affiliation), prev_03, affiliation)) %>%
  select(-affiliation) %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_02), by = c("prev_03" = "affil_alias_02")) %>%
  mutate(prev_03 = ifelse(is.na(affiliation), prev_03, affiliation)) %>%
  select(-affiliation) %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_03), by = c("prev_03" = "affil_alias_03")) %>%
  mutate(prev_03 = ifelse(is.na(affiliation), prev_03, affiliation)) %>%
  select(-affiliation) %>%
  left_join(., select(affils_join_df, affiliation, affil_alias_04), by = c("prev_03" = "affil_alias_04")) %>%
  mutate(prev_03 = ifelse(is.na(affiliation), prev_03, affiliation)) %>%
  select(-affiliation) %>%
  mutate(prev_01 = ifelse(current_affiliation == prev_01, NA, prev_01)) %>%
  mutate(prev_03 = ifelse(prev_03 == prev_02, NA, prev_03)) %>%
  mutate(prev_02 = ifelse(prev_02 == prev_01, NA, prev_02)) %>%
  mutate(prev_01 = ifelse(prev_01 == current_affiliation, NA, prev_01))
  
# TODO change above into method, add affil_alias_03, 04
# TODO add "Independent" to alias

```



### Data Write
```{r data-write}
write.csv(no_duplicates_df, "ReviewerDatabase_Cleaned.csv")
drive_upload("ReviewerDatabase_Cleaned.csv", type= "spreadsheet")

```
